---
title: "scATACseq_src"
author: "Laëtitia"
date: "2022-09-02"
output: html_document
---

# annotation_grange

*OBJECTIVE* = Extract hg38 and hg19 annotations information in R objects

*OUTPUTS* = 
- hg19_annotations_gr.rds
- hg38_annotations_gr.rds

```{r, annotation_grange}

rmarkdown::render(input = "/home/rparmentier/bureau/Git_Metabo_Analysis/bin/annotation_grange.Rmd",
                  output_format = "html_document",
                  output_dir = "/home/rparmentier/Bureau/Git_Metabo_Analysis/html/",
                  output_file = paste0(Sys.Date(), '_', "annotation_grange.html"))


```


# scATACseq_ind_CreateSeuratObject.Rmd

*OBJECTIVE* =  
  
*INPUTS* =   
- [DRUG]_filtered_peak_bc_matrix.h5  
- [DRUG]_singlecell.csv  
- [DRUG]_fragments.tsv.gz  
- hg38_annotation_file.rds ?
  
*OUTPUTS* = 
- list_seurat_obj_annot.rds  
  
```{r}

rmarkdown::render(input = "/home/rparmentier/bureau/Git_Metabo_Analysis/bin/scATACseq_ind_CreateSeuratObject.Rmd",
                  output_format = "html_document",
                  output_dir = "/home/rparmentier/Bureau/Git_Metabo_Analysis/html/",
                  output_file = paste0(Sys.Date(), '_', "scATACseq_ind_CreateSeuratObject.html"))

```


# scATACseq_ind_QualityControl.Rmd

*OBJECTIVE* =  
  
*INPUTS* =   
- list_seurat_obj_annot.rds **(cf. scATACseq_ind_CreateSeuratObject)**  
  
*OUTPUTS* = 
- list_seurat_obj_annot_qc.rds
- list_graphs_qc.rds
- list_seurat_obj_annot_qc_filtered.rds
- [DRUG]_plot_quality_control.svg (OPTIONAL)

```{r}

rmarkdown::render(input = "/home/rparmentier/bureau/Git_Metabo_Analysis/bin/scATACseq_ind_QualityControl.Rmd",
                  output_format = "html_document",
                  output_dir = "/home/rparmentier/Bureau/Git_Metabo_Analysis/html/",
                  output_file = paste0(Sys.Date(), '_', "scATACseq_ind_QualityControl.html"))

```


# scATACseq_merge_MergeObjects.Rmd

*OBJECTIVE* =  
  
*INPUTS* =   
- list_seurat_obj_annot_qc_filtered.rds **(cf. scATACseq_ind_QualityControl.Rmd)**  
- [DRUG]_fragments.tsv.gz  

*OUTPUTS* =   
- seurat_obj_qc_common_merged.rds  
- seurat_obj_qc_merged.rds  
  
```{r}

rmarkdown::render(input = "/home/rparmentier/bureau/Git_Metabo_Analysis/bin/scATACseq_merge_MergeObjects.Rmd",
                  output_format = "html_document",
                  output_dir = "/home/rparmentier/Bureau/Git_Metabo_Analysis/html/",
                  output_file = paste0(Sys.Date(), '_', "scATACseq_merge_MergeObjects.html"))

```


# scATACseq_merge_NormalizationReduction.Rmd

*OBJECTIVE* =  
  
*INPUTS* =   
  
*OUTPUTS* = 
- seurat_obj_qc_common_merged_normalized_reduced.rds    
- seurat_obj_qc_merged_normalized_reduced.rds  
  
```{r}

rmarkdown::render(input = "/home/rparmentier/bureau/Git_Metabo_Analysis/bin/scATACseq_merge_NormalizationReduction.Rmd",
                  output_format = "html_document",
                  output_dir = "/home/rparmentier/Bureau/Git_Metabo_Analysis/html/",
                  output_file = paste0(Sys.Date(), '_', "scATACseq_merge_NormalizationReduction.html"))


```


# scATACseq_merge_CellPeaksStatistics.Rmd

*OBJECTIVE* =    
    
*INPUTS* =     
- seurat_common_merged_qc_normalized_reduced.rds **(cf. scATACseq_merge_NormalizationReduction.Rmd)**   
    
*OUTPUTS* =    
- global_tab_cell.csv  
- statistic_tab_cell.csv   
- nbpeaks_per_cell_plot.svg  
- global_tab_peak.csv  
- statistic_tab_peak.csv  
- nbcell_sharing_peaks_plot.svg  
  
```{r}

rmarkdown::render(input = "/home/rparmentier/bureau/Git_Metabo_Analysis/bin/scATACseq_merge_CellPeaksStatistics.Rmd",
                  output_format = "html_document",
                  output_dir = "/home/rparmentier/Bureau/Git_Metabo_Analysis/html/",
                  output_file = paste0(Sys.Date(), '_', "scATACseq_merge_CellPeaksStatistics.html"))

```

