---
title: "scRNAseq_CITEseq_NeedForBatchEffectCorrection"
author: "Laëtitia Racine"
date: "2022-11-01"
subtitle: "Dernière modification : `r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: "show"
    toc: false
    theme: journal
---


```{r, Setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, Dependencies, message=F, warning=F}

library(dplyr)
library(Seurat)
library(ggplot2)

```

# Script's goal

This code aims at determining if dataset need to be correcting for batch effect bias.

Documentation on the subject : 
- https://satijalab.org/seurat/articles/integration_introduction.html
- https://satijalab.org/seurat/articles/integration_large_datasets.html  
- https://github.com/satijalab/seurat/issues/4753  
- https://github.com/satijalab/seurat/issues/4372  
- https://github.com/satijalab/seurat/discussions/3998  
- https://satijalab.org/seurat/archive/v3.1/integration.html  
- https://blog.bioturing.com/2022/03/24/batch-effect-in-single-cell-rna-seq-frequently-asked-questions-and-answers/  

Question ask on the github forum : https://github.com/satijalab/seurat/issues/6616


```{r, Working directories and external script, warning=F, message=F}

directory = "/home/lracine/Documents/git_brouillon_metabo/"

# Create a unique folder for output corresponding to the date of the day
current_date = format(Sys.time(), "%Y%m%d")
dir.create(path = paste0(directory, "exp/", "scRNAseq_CITEseq_ind_NeedForBatchEffectCorrection/"))
dir.create(path = paste0(directory,"exp/", "scRNAseq_CITEseq_ind_NeedForBatchEffectCorrection/", current_date))
directory_output = paste0(directory, "exp/", "scRNAseq_CITEseq_ind_NeedForBatchEffectCorrection/", current_date, "/")

```

```{r, Input loading}

list_seurat_norm = readRDS(file = "/home/lracine/Documents/Git_Metabo_Analysis/exp/scRNAseq_CITEseq_ind_NormalizeData/20221007/list_seurat_obj_qc_norm.rds")

# Add experiment information 
list_seurat_norm[["CTRL"]]$batch = "batch1"
list_seurat_norm[["DON"]]$batch = "batch1"
list_seurat_norm[["DONaK"]]$batch = "batch1"
list_seurat_norm[["2DG"]]$batch = "batch1"
list_seurat_norm[["2DGaK"]]$batch = "batch1"
list_seurat_norm[["VPA"]]$batch = "batch1"
list_seurat_norm[["CTRLaK"]]$batch = "batch1"
list_seurat_norm[["CTRL2"]]$batch = "batch2"
list_seurat_norm[["AOA"]]$batch = "batch2"
list_seurat_norm[["AOAaK"]]$batch = "batch2"

```


## Process two experiments separately without integration. 
Make UMAP plots where you can see how different samples group.
https://github.com/satijalab/seurat/issues/5761
```{r, fig.width = 20, fig.height = 14}

# Merged the conditions from the same experiment and select variable features
batch1 = c("CTRL", "CTRLaK", "DON", "DONaK", "2DG", "2DGaK", "VPA")
list_batch1 = list_seurat_norm[batch1]
features_batch1 <- SelectIntegrationFeatures(object.list = list_batch1, nfeatures = 3000)
merged_batch1 = merge(x = list_seurat_norm[["CTRL"]], 
                      y = c(list_seurat_norm[["CTRLaK"]], 
                            list_seurat_norm[["DON"]],
                            list_seurat_norm[["DONaK"]], 
                            list_seurat_norm[["2DG"]],
                            list_seurat_norm[["2DGaK"]], 
                            list_seurat_norm[["VPA"]]))
VariableFeatures(merged_batch1) <- features_batch1

batch2 = c("CTRL2", "AOA", "AOAaK")
list_batch2 = list_seurat_norm[batch2]
features_batch2 <- SelectIntegrationFeatures(object.list = list_batch2, nfeatures = 3000)
merged_batch2 = merge(x = list_seurat_norm[["CTRL2"]], 
                      y = c(list_seurat_norm[["AOAaK"]], 
                            list_seurat_norm[["AOA"]]))
VariableFeatures(merged_batch2) <- features_batch2

rm(list_batch1, list_batch2, batch1, batch2)

# Run PCA and UMAP on each experiment
merged_batch1 = RunPCA(object = merged_batch1,
                       assay = "SCT",
                       reduction.name = "pca",
                       npcs = 100,
                       verbose = TRUE)
merged_batch2 = RunPCA(object = merged_batch2,
                       assay = "SCT",
                       reduction.name = "pca",
                       npcs = 100,
                       verbose = TRUE)

merged_batch1 = RunUMAP(object = merged_batch1, 
                        assay = "SCT",
                        reduction =  "pca",
                        dims = 1:30,
                        reduction.name = "umap", 
                        verbose = TRUE)
merged_batch2 = RunUMAP(object = merged_batch2, 
                        assay = "SCT",
                        reduction =  "pca",
                        dims = 1:30,
                        reduction.name = "umap", 
                        verbose = TRUE)


# Show all conditions independently
batch1_umap_plot = DimPlot(object = merged_batch1, 
                           group.by = "orig.ident", 
                           reduction = "umap")
batch1_umap_split_plot = DimPlot(object = merged_batch1, 
                                 group.by = "orig.ident", 
                                 split.by = "orig.ident", 
                                 reduction = "umap")

batch2_umap_plot = DimPlot(object = merged_batch2, 
                          group.by = "orig.ident", 
                          reduction = "umap")
batch2_umap_split_plot = DimPlot(object = merged_batch2, 
                                group.by = "orig.ident", 
                                split.by = "orig.ident", 
                                reduction = "umap")

batch1_umap_plot / batch1_umap_split_plot
batch2_umap_plot / batch2_umap_split_plot

# saveRDS(merged_batch1, file = paste0(directory_output, "merged_batch1_reduc.rds"))
# saveRDS(merged_batch2, file = paste0(directory_output, "merged_batch2_reduc.rds"))
ggsave(batch1_umap_plot / batch1_umap_split_plot, 
       file = paste0(directory_output, "umap_batch1.png"),
       width = 20, height = 14)
ggsave(batch2_umap_plot / batch2_umap_split_plot, 
       file = paste0(directory_output, "umap_batch2.png"),
       width = 20, height = 14)

rm(merged_batch1, merged_batch2, features_batch1, features_batch2)
rm(batch1_umap_plot, batch1_umap_split_plot, batch2_umap_plot, batch2_umap_split_plot)
gc()

```

## Process two experiment together without integration.
Make same UMAP plots where you can see individual samples and experiment groups.
```{r}

# Merged all the conditions from the two experiments and select variable features
features_all <- SelectIntegrationFeatures(object.list = list_seurat_norm, nfeatures = 3000)
merged_all = merge(x = list_seurat_norm[["CTRL"]], 
                      y = c(list_seurat_norm[["CTRLaK"]], 
                            list_seurat_norm[["DON"]],
                            list_seurat_norm[["DONaK"]], 
                            list_seurat_norm[["2DG"]],
                            list_seurat_norm[["2DGaK"]], 
                            list_seurat_norm[["VPA"]],
                            list_seurat_norm[["CTRL2"]],
                            list_seurat_norm[["AOA"]],
                            list_seurat_norm[["AOAaK"]]))
VariableFeatures(merged_all) <- features_all

# Run PCA and UMAP
merged_all = RunPCA(object = merged_all,
                       assay = "SCT",
                       reduction.name = "pca",
                       npcs = 100,
                       verbose = TRUE)
merged_all = RunUMAP(object = merged_all, 
                        assay = "SCT",
                        reduction =  "pca",
                        dims = 1:30,
                        reduction.name = "umap", 
                        verbose = TRUE)

# Show the conditions
umap_plot = DimPlot(object = merged_all, 
                           group.by = "orig.ident", 
                           reduction = "umap")
umap_plot_batch = DimPlot(object = merged_all, 
                           group.by = "batch", 
                           reduction = "umap")
umap_split_plot = DimPlot(object = merged_all, 
                                 group.by = "orig.ident", 
                                 split.by = "orig.ident", 
                                 reduction = "umap")

umap_plot / umap_plot_batch /umap_split_plot

merged_ctrl = subset(merged_all, subset = orig.ident %in% c("CTRL", "CTRL2"))
umap_ctrl =  DimPlot(object = merged_ctrl, 
                     group.by = "orig.ident", 
                     reduction = "umap")
umap_split_ctrl = DimPlot(object = merged_ctrl, 
                                 group.by = "orig.ident", 
                                 split.by = "orig.ident", 
                                 reduction = "umap")
umap_ctrl / umap_split_ctrl

# saveRDS(merged_all, file = paste0(directory_output, "merged_all_reduc.rds"))
ggsave(umap_plot / umap_plot_batch, 
       file = paste0(directory_output, "umap_bothbatch.png"),
       width = 20, height = 14)
ggsave(umap_split_plot, 
       file = paste0(directory_output, "umap_bothbatch_split.png"),
       width = 20, height = 8)
ggsave(umap_ctrl / umap_split_ctrl, 
       file = paste0(directory_output, "umap_bothbatch_ctrl.png"),
       width = 20, height = 14)

rm(merged_all, merged_ctrl, features_all)
rm(umap_ctrl, umap_split_ctrl, umap_plot, umap_plot_batch, umap_split_plot)
gc()

```

## Work only with the controls on SCT
```{r, fig.width = 12, fig.height = 14}

# Extract the two controls from the list of seurat object
CTRL_manip1 = list_seurat_norm[["CTRL"]]
CTRL_manip2 = list_seurat_norm[["CTRL2"]]

# Merged all the conditions from the two experiments and select variable features
features_ctrl <- SelectIntegrationFeatures(object.list = list(CTRL_manip1, CTRL_manip2), nfeatures = 3000)
merged = merge(x = CTRL_manip1, y = CTRL_manip2)
VariableFeatures(merged) <- features_ctrl

# Run PCA and UMAP
merged = RunPCA(object = merged,
                       assay = "SCT",
                       reduction.name = "pca",
                       npcs = 100,
                       verbose = TRUE)
merged = RunUMAP(object = merged, 
                        assay = "SCT",
                        reduction =  "pca",
                        dims = 1:30,
                        reduction.name = "umap", 
                        verbose = TRUE)

# Show the ocnditions
ctrl_umap_plot = DimPlot(object = merged, 
                           group.by = "orig.ident", 
                           reduction = "umap")
ctrl_split_plot = DimPlot(object = merged, 
                                 group.by = "orig.ident", 
                                 split.by = "orig.ident", 
                                 reduction = "umap")

ctrl_umap_plot / ctrl_split_plot

ggsave(ctrl_umap_plot / ctrl_split_plot, 
       file = paste0(directory_output, "umap_ctrl_merged_sct.png"),
       width = 20, height = 14)


```

## Work with only the controls on logNormalisation
```{r, fig.width = 14, fig.height = 16}

# Extract the two controls from the list of seurat object
CTRL_manip1 = list_seurat_norm[["CTRL"]]
CTRL_manip2 = list_seurat_norm[["CTRL2"]]

# Merge both control objects
CTRL_merged = merge(x = CTRL_manip1, 
                    y = CTRL_manip2, 
                    add.cell.ids = c("CTRL1", "CTRL2"))

# Visualize control objects in UMAP and PCA
DefaultAssay(CTRL_merged) = "RNA"
# CTRL_merged = NormalizeData(CTRL_merged)
CTRL_merged = FindVariableFeatures(CTRL_merged)
CTRL_merged = ScaleData(CTRL_merged)
CTRL_merged = RunPCA(CTRL_merged, npcs = 30)
CTRL_merged = RunUMAP(CTRL_merged, reduction = "pca", dims = 1:30)

umap_batch = DimPlot(object = CTRL_merged, 
                     group.by = "orig.ident", 
                    reduction = "umap")
umap_split = DimPlot(object = CTRL_merged, 
                     group.by = "orig.ident",
                    split.by = "orig.ident", 
                    reduction = "umap") + NoLegend()

umap_batch | umap_split

ggsave(umap_batch / umap_split, 
       file = paste0(directory_output, "umap_ctrl_merged_log.png"),
       width = 20, height = 14)

```


```{r, Rsession}

# Clean working space and show package version
# rm(list = ls())
# sessionInfo()

```





